### 2021-09-28 data-raw/data-preprocessing.Rmd
vignette:  input to valid

```
```{r wages-demog-hs}
# join the wages information and the demographic information by case id.
wages_demog <- left_join(mean_hourly_wage, full_demographics, by="id")
# calculate the years in work force and the age of the subjects in 1979
wages_demog <- wages_demog %>%
  mutate(yr_hgc = as.numeric(yr_hgc)) %>%
  mutate(years_in_workforce = year - yr_hgc) %>%
  mutate(age_1979 = 1979 - (dob_year + 1900))
# filter only the id with high school education
wages_before <- wages_demog  %>% filter(grepl("GRADE", hgc))
# calculate the number of observation
keep_me <- wages_before %>%
  count(id) %>%
  filter(n > 4)
wages_before <- wages_before %>%
  filter(id %in% keep_me$id)
```

>>>>

```
```{r wages-demog-hs}
# join the wages information and the demographic information by case id.
wages_demog <- left_join(mean_hourly_wage, full_demographics, by="id")
# calculate the years in work force and the age of the subjects in 1979
wages_demog <- wages_demog %>%
  mutate(yr_hgc = as.numeric(yr_hgc)) %>%
  mutate(years_in_workforce = year - yr_hgc) %>%
  mutate(age_1979 = 1979 - (dob_year + 1900))
# filter only the id with high school education
wages_before <- wages_demog  %>% filter(grepl("GRADE", hgc))
# calculate the number of observation
keep_me <- wages_before %>%
  count(id) %>%
  filter(n > 4)
wages_before <- wages_before %>%
  filter(id %in% keep_me$id)

```
```{r save-data, echo = FALSE, eval = FALSE}
saveRDS(wages_before, here::here("paper/results/wages_before.rds"))
```
